---
title: "Importing Data"
author: Shannon Coyle
output: html_notebook
---

## Load installed packages into this working session, called putting them into this library.
You need to do this every time you reopen a Rmd file or start a new one.
```{r, message=FALSE}
library(mosaic)
library(haven)
library(ggpubr)
library(readxl)
library(Rlab)
library(boot)

library(randtests)
library(snpar)
```

```{r}
# function to take in a vector of 0s and 1s and calculate cmax
cmax <- function(v) {
  # set count.zero to be 0
  count.zero <- 0
  
  # set max to be empty vector
  max <- c()
  
  for (i in 1:length(v)) {

    # if it's a miss: count goes up, count is added to max vector, cmax takes the maximum of all values
    if (v[i] == 1) {
      count.zero <- count.zero + 1
      max[i] <- count.zero
      } 
    else {
    # if it's a hit count added is 0
        count.zero <- 0
        max[i] <- 0
      }
    suppressWarnings(cmax <- max(max))
  }
  
  # return calculated value of cmax
  return(cmax)
}
```

# count number of individual misses (number of 1's)
```{r}
totalMiss <- function(v) {
  # set hit and miss count to 0
  count.miss <- 0 
  count.hit <- 0
  
  miss <- c()
  
  for (i in 1:length(v)) {

    # if it's a miss: count goes up, count is added to max vector, cmax takes the maximum of all values
    if (v[i] == 1) {
      count.miss <- count.miss + 1
      miss[i] <- count.miss
      } 
    else {
    # if it's a hit count added is 0
        count.hit <- 0
        miss[i] <- 0
      }
    suppressWarnings(totalMisses <- max(miss))
  }
  
  # return calculated value of total misses
  return(totalMisses)
  
}
```

# counting how many miss streaks there are
```{r}
missStreak <- function(v) {
 count.one <- 0
  
  count.streaks <- 0
  
  num.miss <- c()
  
  counts <- c()
  
  for (i in 1:length(v)) {
    # if it's a miss: count goes up, count is added to counts vector, fills num.miss with a 1
    if (v[i] == 1) {
      count.one <- count.one + 1
      counts[i] <- count.one
      num.miss[i] <- 1
      } 
    else {
    # if it's a hit count added is 0, count is added to counts vector, fills num.miss with a 0
        count.one <- 0
        counts[i] <- count.one + 0
        num.miss[i] <- 0
      }
    }
  
  for (j in 2:length(v)) {
    if (counts[j] == 0 && counts[j-1] != 0) {
      count.streaks <- count.streaks + 1
      } 
    else {
        count.streaks <- count.streaks + 0
      }
  }
  return(count.streaks)
}
```

# Calculating Method 1
```{r}
method1 <- function(v) {
  proportion <- c()
  
  proportion <- missStreak(v)/totalMiss(v)
  
  return(proportion)
}
```

## METHOD 2
# count number of hits between misses
```{r}
method2 <- function(v) {
  # set number of hits to 0
  count.hit <- 0
  
  # make an empty vector
  hits <- c()
  
  j  <- 1
  
  distance <- c()
  
  for(i in 1:length(v)) {
    # if a hit, count increases 
    if (isTRUE(v[1] == 0)) {
      
    }
    
    if(v[i] == 0) {
      count.hit <- count.hit + 1
      hits[i] <- count.hit
    }
    else
    {
      count.hit <- 0
      hits[i] <- count.hit
    }
    for (j in 1:length(v)-1) {
      if (isTRUE(hits[i] == 0 & hits[i+j] == 0)) {
        distance[i] <- hits[i+j-1]
        j <- j+1
        } else {
          j<- j+1
        }
      }
    suppressWarnings(numHits <- hits)
  }
 
   distance <- distance[!is.na(distance)]
  distance <- distance[distance!=0]
  
  if (v[1] == 0) {
    distance <- distance[2:length(song.a)]
    distance <- distance[!is.na(distance)]
  } 
  else {
    distance <- distance
  }
  
  return(distance)
}
```

# runs the "runstest" on the data
```{r}
methodRuns <- function(v) {
  threshold = median(v)
  
  runs.test(v, alternative = "two.sided", threshold)
}
```

# performing a serial test
```{r}
serialMethod <- function(v) {
  count <- 0
  j <- 1
  
  hits <- c()
  distance <- c()
  
  
  for (i in 1:length(v)) {
    if (isTRUE(v[i] == 0 && v[i + 1] == 1)) {
      count <- count + 1
      hits[i] <- count
    }
    else {
      count <- 0
      hits[i] <- count
    }
    
    for (j in 1:length(v)-1) {
      if (isTRUE(hits[i] == 0 & hits[i+j] == 0)) {
        distance[i] <- hits[i+j-1]
        j <- j+1
        } else {
          j<- j+1
        }
      }
    suppressWarnings(numHits <- hits)
  }
  
  distance <- distance[!is.na(distance)]
  distance <- distance[distance!=0]
  
  if (v[1] == 0 && v[2] == 1) {
    distance <- distance[2:length(song.a)]
    distance <- distance[!is.na(distance)]
  } 
  else {
    distance <- sum(distance)
  }
  return(distance)
}
```

# Imports the AmericanGirl.txt file (FILE 1/7)
```{r}
# Finds the path of the data file and brings it into R
americanGirl <- read.delim(file = "D:/Documents/Desktop/Monmouth/FA_2020/MA380/Project/ActualSongFiles/AmericanGirl.txt", header = TRUE, sep = " ")

# Has all of the data be read as a number <- needed to do this so the "median" function would work
americanGirl.data <- as.numeric(americanGirl)

# Prints out the imported data
head(americanGirl)
```

# testing method 1
```{r}
cat('Americal Girl: ', '\n', 
  'Total Misses: ', totalMiss(americanGirl.data), '\n', 
    'Total Number of Miss Streaks: ', missStreak(americanGirl.data), '\n', '\n')

cat('\n', '--- CALCULATIONS FOR METHOD 1 ---', '\n')
cat('American Girl: ', method1(americanGirl.data), '\n')
```

# testing method 2
```{r}
cat('\n', '--- CALCULATIONS FOR METHOD 2 ---', '\n')
cat('American Girl: ', method2(americanGirl.data), '\n')
```

# testing the runs method
```{r}
cat('\n', '--- CALCULATIONS FOR RUNS TEST ---', '\n')
methodRuns(americanGirl.data)
```

# testing the serial method
```{r}
serialMethod(americanGirl.data)
```
# Imports the Funky.txt file (FILE 2/7)
```{r}
# Finds the path of the data file and brings it into R
funky <- read.delim(file = "D:/Documents/Desktop/Monmouth/FA_2020/MA380/Project/ActualSongFiles/Funky.txt", header = TRUE, sep = " ")

# Has all of the data be read as a number <- needed to do this so the "median" function would work
funky.data <- as.numeric(funky)

# Prints out the imported data
head(funky)
```

# testing method 1
```{r}
cat('Funky: ', '\n', 
  'Total Misses: ', totalMiss(funky.data), '\n', 
    'Total Number of Miss Streaks: ', missStreak(funky.data), '\n', '\n')

cat('\n', '--- CALCULATIONS FOR METHOD 1 ---', '\n')
cat('Funky: ', method1(funky.data), '\n')
```

# testing method 2
```{r}
cat('\n', '--- CALCULATIONS FOR METHOD 2 ---', '\n')
cat('Funky: ', method2(funky.data), '\n')
```

# testing the runs method
```{r}
cat('\n', '--- CALCULATIONS FOR RUNS TEST ---', '\n')
methodRuns(funky.data)
```

# testing the serial method
```{r}
serialMethod(funky.data)
```

# Imports the Hurts.txt file (FILE 3/7)
```{r}
# Finds the path of the data file and brings it into R
hurts <- read.delim(file = "D:/Documents/Desktop/Monmouth/FA_2020/MA380/Project/ActualSongFiles/Hurts.txt", header = FALSE, sep = " ")

# Has all of the data be read as a number <- needed to do this so the "median" function would work
hurts.data <- as.numeric(hurts)

# Prints out the imported data
head(hurts)
```

# testing method 1
```{r}
cat('Hurts: ', '\n', 
  'Total Misses: ', totalMiss(hurts.data), '\n', 
    'Total Number of Miss Streaks: ', missStreak(hurts.data), '\n', '\n')

cat('\n', '--- CALCULATIONS FOR METHOD 1 ---', '\n')
cat('Hurts: ', method1(hurts.data), '\n')
```

# testing method 2
```{r}
cat('\n', '--- CALCULATIONS FOR METHOD 2 ---', '\n')
cat('Hurts: ', method2(hurts.data), '\n')
```

# testing the runs method
```{r}
cat('\n', '--- CALCULATIONS FOR RUNS TEST ---', '\n')
methodRuns(hurts.data)
```

# testing the serial method
```{r}
serialMethod(hurts.data)
```

# Imports the Judith.txt file (FILE 4/7)
```{r}
# Finds the path of the data file and brings it into R
judith <- read.delim(file = "D:/Documents/Desktop/Monmouth/FA_2020/MA380/Project/ActualSongFiles/Judith.txt", header = TRUE, sep = " ")

# Has all of the data be read as a number <- needed to do this so the "median" function would work
judith.data <- as.numeric(judith)

# Prints out the imported data
head(judith)
```

# testing method 1
```{r}
cat('Judith: ', '\n', 
  'Total Misses: ', totalMiss(judith.data), '\n', 
    'Total Number of Miss Streaks: ', missStreak(judith.data), '\n', '\n')

cat('\n', '--- CALCULATIONS FOR METHOD 1 ---', '\n')
cat('Judith: ', method1(judith.data), '\n')
```

# testing method 2
```{r}
cat('\n', '--- CALCULATIONS FOR METHOD 2 ---', '\n')
cat('Judith: ', method2(judith.data), '\n')
```

# testing the runs method
```{r}
cat('\n', '--- CALCULATIONS FOR RUNS TEST ---', '\n')
methodRuns(judith.data)
```

# testing the serial method
```{r}
serialMethod(judith.data)
```

## IMPLEMENTING A PARAMETRIC BOOTSTRAP
# with a Bernoulli distribution
```{r}
boot.dist <- 100

parametricBootstrap <- function(v) {
  sample.diffmedian <- median(v)
  
  sampled <- matrix(nrow = boot.dist, ncol = length(v))
  
  for (j in 1:length(v)) {
    for (i in 1:boot.dist) {
      sampled[i, j] <- (sample(rbern(length(v), .50)))[j]
    }
  }
  
  return(sampled)
}
```

# Cmax with the bootstrap
```{r}
cmax.test <- function(m, song) {
  cmax.vals <- c()
  
  for (i in 1:nrow(m)) {
    cmax.vals[i] <- cmax(m[i,])
  }
  cmax.test.stat <- cmax(song)
  
  pval <- 2*min(sum(cmax.vals >= cmax.test.stat), sum(cmax.vals <= cmax.test.stat))/1000
  return(pval)
}
```

## Num of Misses / Num of Miss Streaks on Resampled Data
```{r}
method1.test <- function(m,song) {
  method1.vals <- c()
  
  for (i in 1:nrow(m)) {
    method1.vals[i] <- method1(m[i,])
  }
  
  method1.test.stat <- method1(song)
  
  pval <- 2*min(sum(method1.vals >= method1.test.stat), sum(method1.vals <= method1.test.stat))/1000
  return(pval)
}
```

# method 2 on resampled data
```{r}
method2.test <- function(m, song) {
  method2.vals <- c()
  
 
  for(i in 1:nrow(m)) {
    method2.vals <- method2(m[i,])
  }
  
  method2.test.stat <- method2(song)
  
  suppressWarnings(pval <- 2 * min(sum(method2.vals >= method2.test.stat), sum(method2.vals <= method2.test.stat)) / 1000)
  return(pval)
}
```

# runs test on resampled data
```{r}
methodRuns.test <- function(m) {
  methodRuns.vals <- c()

  for(i in 1:nrow(m)) {
    methodRuns.vals <- methodRuns(m[i,])
  }

  return(methodRuns.vals)
}
```

```{r}
# function to compute distances on each row of resampled matrix
samples.numHits <- function(m) {
  numHits.vals <- vector(mode = "list", length = nrow(m))
    for (i in 1:nrow(m)) {
      numHits.vals[[i]] <- method2(m[i,])
    }
  return(numHits.vals)
}
```

```{r}
# function to compute runs.test on distances
runs.test.numHits <- function(list) {
  
  distances <- Reduce(c,list)
  
  test <- runs.test(distances)
  pval <- test$p.value
  stat <- test$statistic
  
  return(c(pval, stat))
}
```

# serial method on resampled data
```{r}
serialMethod.test <- function(m) {
  serialMethod.vals <- c()
  
  for(i in 1:nrow(m)) {
    serialMethod.vals <- serialMethod(m[i,])
  }
  
  return(serialMethod.vals)
}
```

```{r}
americanGirl.samples <- parametricBootstrap(americanGirl.data)
```

# testing the bootstrap cmax function
```{r}
cmax.test(americanGirl.samples, americanGirl.data)
```

## Pvalue
```{r}
method1.test(americanGirl.samples, americanGirl.data)
```

```{r}
start_time <- Sys.time()
method2.test(americanGirl.samples, americanGirl.data)
end_time <- Sys.time()

end_time - start_time
```

# testing serial method on resampled data
```{r}
start_time <- Sys.time()
serialMethod.test(americanGirl.samples)
end_time <- Sys.time()

end_time - start_time
```

#testing median of distance vector - SONG A
```{r}
start_time <- Sys.time()
runs.test.numHits(samples.numHits(americanGirl.samples))
end_time <- Sys.time()

end_time - start_time
```
```{r}
funky.samples <- parametricBootstrap(funky.data)
```

# testing the bootstrap cmax function
```{r}
cmax.test(funky.samples, funky.data)
```

## Pvalue
```{r}
method1.test(funky.samples, funky.data)
```

```{r}
start_time <- Sys.time()
method2.test(funky.samples, funky.data)
end_time <- Sys.time()

end_time - start_time
```

# testing serial method on resampled data
```{r}
start_time <- Sys.time()
serialMethod.test(funky.samples)
end_time <- Sys.time()

end_time - start_time
```

#testing median of distance vector - SONG A
```{r}
start_time <- Sys.time()
runs.test.numHits(samples.numHits(funky.samples))
end_time <- Sys.time()

end_time - start_time
```

```{r}
hurts.samples <- parametricBootstrap(hurts.data)
```

# testing the bootstrap cmax function
```{r}
cmax.test(hurts.samples, hurts.data)
```

## Pvalue
```{r}
method1.test(hurts.samples, hurts.data)
```

```{r}
start_time <- Sys.time()
method2.test(hurts.samples, hurts.data)
end_time <- Sys.time()

end_time - start_time
```

# testing serial method on resampled data
```{r}
start_time <- Sys.time()
serialMethod.test(hurts.samples)
end_time <- Sys.time()

end_time - start_time
```

#testing median of distance vector - SONG A
```{r}
start_time <- Sys.time()
runs.test.numHits(samples.numHits(hurts.samples))
end_time <- Sys.time()

end_time - start_time
```

# bootstrapping "Judith"
```{r}
judith.samples <- parametricBootstrap(judith.data)
```

# testing the bootstrap cmax function
```{r}
cmax.test(judith.samples, judith.data)
```

## Pvalue
```{r}
method1.test(judith.samples, judith.data)
```

```{r}
start_time <- Sys.time()
method2.test(judith.samples, judith.data)
end_time <- Sys.time()

end_time - start_time
```

# testing serial method on resampled data
```{r}
start_time <- Sys.time()
serialMethod.test(judith.samples)
end_time <- Sys.time()

end_time - start_time
```

#testing median of distance vector - SONG A
```{r}
start_time <- Sys.time()
runs.test.numHits(samples.numHits(judith.samples))
end_time <- Sys.time()

end_time - start_time
```