---
title: "Method 1"
author: Shannon Coyle
output: html_notebook
---

## Load installed packages into this working session, called putting them into this library.
You need to do this every time you reopen a Rmd file or start a new one.
```{r, message=FALSE}
library(mosaic)
library(haven)
library(ggpubr)
library(readxl)
library(Rlab)
library(boot)
```

```{r}
# function to take in a vector of 0s and 1s and calculate cmax
cmax <- function(v) {
  # set count.zero to be 0
  count.zero <- 0
  
  # set max to be empty vector
  max <- c()
  
  for (i in 1:length(v)) {

    # if it's a miss: count goes up, count is added to max vector, cmax takes the maximum of all values
    if (v[i] == 1) {
      count.zero <- count.zero + 1
      max[i] <- count.zero
      } 
    else {
    # if it's a hit count added is 0
        count.zero <- 0
        max[i] <- 0
      }
    suppressWarnings(cmax <- max(max))
  }
  
  # return calculated value of cmax
  return(cmax)
}
```

# count number of individual misses (number of 1's)
```{r}
totalMiss <- function(v) {
  # set hit and miss count to 0
  count.miss <- 0 
  count.hit <- 0
  
  miss <- c()
  
  for (i in 1:length(v)) {

    # if it's a miss: count goes up, count is added to max vector, cmax takes the maximum of all values
    if (v[i] == 1) {
      count.miss <- count.miss + 1
      miss[i] <- count.miss
      } 
    else {
    # if it's a hit count added is 0
        count.hit <- 0
        miss[i] <- 0
      }
    suppressWarnings(totalMisses <- max(miss))
  }
  
  # return calculated value of total misses
  return(totalMisses)
  
}
```

# counting how many miss streaks there are
```{r}
missStreak <- function(v) {
 count.one <- 0
  
  count.streaks <- 0
  
  num.miss <- c()
  
  counts <- c()
  
  for (i in 1:length(v)) {
    # if it's a miss: count goes up, count is added to counts vector, fills num.miss with a 1
    if (v[i] == 1) {
      count.one <- count.one + 1
      counts[i] <- count.one
      num.miss[i] <- 1
      } else {
    # if it's a hit count added is 0, count is added to counts vector, fills num.miss with a 0
        count.one <- 0
        counts[i] <- count.one + 0
        num.miss[i] <- 0
      }
    }
  for (j in 2:length(v)) {
    if (counts[j] == 0 && counts[j-1] != 0) {
      count.streaks <- count.streaks + 1
      } else {
        count.streaks <- count.streaks + 0
      }
  }
  return(count.streaks)
}
```

# Calculating Method 1
```{r}
method1 <- function(v) {
  proportion <- c()
  
  proportion <- missStreak(v)/totalMiss(v)
  
  return(proportion)
}
```


```{r}
song.a <- c(1,0,0,0,0,0,1,0,1,0,0,1,0,0,0,0,1,0,0,0)
song.b <- c(0,0,0,1,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0)
song.c <- c(1,0,1,0,1,0,0,0,0,1,1,0,0,0,0,0,0)
song.d <- c(1,1,1,1,0,1,1,1,1,1,1,1,1,0,0,1,0)

cat('SONG A: ', '\n', 
  'Total Misses: ', totalMiss(song.a), '\n', 
    'Total Number of Miss Streaks: ', missStreak(song.a), '\n', '\n')

cat('SONG B: ', '\n', 
  'Total Misses: ', totalMiss(song.b), '\n', 
     'Total Number of Miss Streaks: ', missStreak(song.b), '\n', '\n')

cat('SONG C: ', '\n', 
  'Total Misses: ', totalMiss(song.c), '\n', 
    'Total Number of Miss Streaks: ', missStreak(song.c), '\n', '\n')

cat('SONG D: ', '\n', 
  'Total Misses: ', totalMiss(song.d), '\n', 
    'Total Number of Miss Streaks: ', missStreak(song.d), '\n', '\n')

cat('\n', '--- CALCULATIONS FOR METHOD 1 ---', '\n')
cat('Song A: ', method1(song.a), '\n')
cat('Song B: ', method1(song.b), '\n')
cat('Song C: ', method1(song.c), '\n')
cat('Song D: ', method1(song.d), '\n')
```

## METHOD 2
# count number of hits between misses
```{r}
method2 <- function(v) {
  # set number of hits to 0
  count.hit <- 0
  distance <- c()
  n <- 0
  
  # make an empty vector
  hits <- c()
  
  for (j in 1:length(v)) {
    for (i in 1:length(v)) {
      # if a hit, count increases
      if (v[i] == 0) {
        count.hit <- count.hit + 1
        hits[i] <- count.hit
      }
      else
      {
        count.hit <- 0
        hits[i] <- count.hit
      }
      suppressWarnings(numHits <- hits[i])
    }
    distance <- numHits[j]
  }
  
  return(distance)
}
```

## IMPLEMENTING A PARAMETRIC BOOTSTRAP
# with a Bernoulli distribution
```{r}
boot.dist <- 1000

parametricBootstrap <- function(v) {
  sample.diffmedian <- median(v)
  
  sampled <- matrix(nrow = boot.dist, ncol = length(v))
  
  for (j in 1:length(v)) {
    for (i in 1:boot.dist) {
      sampled[i, j] <- (sample(rbern(length(v), .50)))[j]
    }
  }
  
  return(sampled)
}
```

# testing Parametric bootstrap function
```{r}
song.a <- c(1,0,0,0,0,0,1,0,1,0,0,1,0,0,0,0,1,0,0,0)

#parametricBootstrap(song.a)
```

# testing method 2
```{r}
song.a <- c(1,0,0,0,0,0,1,0,1,0,0,1,0,0,0,0,1,0,0,0)

method2(song.a)
```

# Cmax with the bootstrap
```{r}
cmax.test <- function(m, song) {
  cmax.vals <- c()
  
  for (i in 1:nrow(m)) {
    cmax.vals[i] <- cmax(m[i,])
  }
  cmax.test.stat <- cmax(song)
  
  pval <- 2*min(sum(cmax.vals >= cmax.test.stat), sum(cmax.vals <= cmax.test.stat))/1000
  return(pval)
}
```

# testing the functions with a Parametric bootstrap
```{r}
song.a <- c(1,0,0,0,0,0,1,0,1,0,0,1,0,0,0,0,1,0,0,0)
song.b <- c(0,0,0,1,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0)
song.c <- c(1,0,1,0,1,0,0,0,0,1,1,0,0,0,0,0,0)

songAParam <- parametricBootstrap(song.a)
songBParam <- parametricBootstrap(song.b)
songCParam <- parametricBootstrap(song.c)
```

# testing the bootstrap cmax function
```{r}
cmax.test(songAParam, song.a)
cmax.test(songBParam, song.b)
cmax.test(songCParam, song.c)
```

## Num of Misses / Num of Miss Streaks on Resampled Data
```{r}
method1.test <- function(m,song) {
  method1.vals <- c()
  for (i in 1:nrow(m)) {
    method1.vals[i] <- miss.over.streaks(m[i,])
  }
  method1.test.stat <- miss.over.streaks(song)
  pval <- 2*min(sum(method1.vals >= method1.test.stat), sum(method1.vals <= method1.test.stat))/1000
  return(pval)
}
```

## Pvalue
```{r}
method1.test(songAParam, song.a)
method1.test(songBParam, song.b)
method1.test(songCParam, song.c)
```