---
title: "Research Problem"
author: "Sam Colucci"
output:
  pdf_document: default
  html_notebook: default
---

# Computing Cmax test statistic

Cmax: denotes the maximum number of consecutive misses in a song
*(somewhat) works so that in songs where all of the misses are in the same region, there would be a higher probability of a longer string of consecutive misses (higher Cmax) than where the same number of misses would occur at random in a song of the same length.


```{r}
# function to take in a vector of 0s and 1s and calculate cmax
cmax <- function(v) {
  
  # set count.one to be 0
  count.one <- 0
  
  # set max to be empty vector
  max <- c()
  
  for (i in 1:length(v)) {

    # if it's a miss: count goes up, count is added to max vector, cmax takes the maximum of all values
    if (v[i] == 1) {
      count.one <- count.one + 1
      max[i] <- count.one
      } else {
    # if it's a hit count added is 0
        count.one <- 0
        max[i] <- 0
      }
    suppressWarnings(cmax <- max(max))
  }
  print(max)
  # return calculated value of cmax
  return(cmax)
}
```


```{r}
song.a <- c(1,0,0,0,0,0,1,0,1,0,0,1,0,0,0,0,1,0,0,0)
song.b <- c(0,0,0,1,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0)
song.c <- c(1,0,1,0,1,0,0,0,0,1,1,0,0,0,0,0,0)
song.d <- c(1,1,1,1,0,1,1,1,1,1,1,1,1,0,0,1,0)

cmax(song.a)
cmax(song.b)
cmax(song.c)
cmax(song.d)
```


# Method 1

Compute number of total misses over the number of miss streaks

```{r}
# function to take in a vector of 0s and 1s and calculate cmax
miss.over.streaks <- function(v) {
  
  count.one <- 0
  
  count.streaks <- 0
  
  num.miss <- c()
  
  counts <- c()
  
  for (i in 1:length(v)) {

    # if it's a miss: count goes up, count is added to counts vector, fills num.miss with a 1
    if (v[i] == 1) {
      count.one <- count.one + 1
      counts[i] <- count.one
      num.miss[i] <- 1
      } else {
    # if it's a hit count added is 0, count is added to counts vector, fills num.miss with a 0
        count.one <- 0
        counts[i] <- count.one + 0
        num.miss[i] <- 0
      }
    }
  for (j in 2:length(v)) {
    if (counts[j] == 0 && counts[j-1] != 0) {
      count.streaks <- count.streaks + 1
      } else {
        count.streaks <- count.streaks + 0
      }
  }
  prop <- sum(num.miss)/count.streaks
  # return calculated value of proportion
  return(prop)
}
```

```{r}
miss.over.streaks(song.a)
miss.over.streaks(song.b)
miss.over.streaks(song.c)
miss.over.streaks(song.d)
```

# Method 2

Compute the distance in between every miss

```{r}
distance.funct <- function(v) {
  
  distance.vect <- c()
  distance <- 0
  
  for (i in 1:length(v)) {
    if (v[i] == 1 && v[i+1] == 1) {
      distance <- distance +1
      distance.vect[i] <- distance
    } else if (v[i-1] == 0 && v[i] == 1 && v[i+1] == 0) {
      distance <- 0
      distance.vect[i] <- 1
    } else if ((v[i] == 0 && v[i+1] ==0) %% (v[i] == 0 && v[i+1] == 1)) {
      distance <- 0
      distance.vect[i] <- 0
    }
  }
  return(distance.vect)
}
```

```{r}
distance.funct(song.a)
```


```{r}
# function to take in a vector of 0s and 1s and calculate cmax
distance <- function(v) {
  
  # set count.one to be 0
  count.one <- 0
  
  # set max to be empty vector
  max <- c()
  s <- 0
  
  for (i in 1:length(v)) {

    # if it's a miss: count goes up, count is added to max vector, cmax takes the maximum of all values
    if (v[i] == 0) {
      count.one <- count.one + 1
      max[i] <- count.one
      } else {
    # if it's a hit count added is 0
        count.one <- 0
        max[i] <- 0
      }
  for (j in 1:length(max)) {
    if (max[i+s] != 0)
      
  
    cmax <- max(max)
  }
  print(max)
  # return calculated value of cmax
  return(cmax)
}
```

```{r}
distance(song.a)
```



```{r}
distance <- function(v) {
  num.zero <- c()
  for (i in 1:length(v)) {
    if (v[i] == 0) {
      num.zero[i] <- 1
    } else {
      num.zero[i] <- 0
    }
  }
    return(num.zero)
}
  # for (j in 1:length(num.zero)) {
  #   if (num.zero[j] == 1) {
  #     distance.vect[j] <- sum(num.zero[1:j])
  #   }
  # }
```

```{r}
distance(song.b)
```

