---
title: "Research Problem"
author: "Sam Colucci"
output:
  pdf_document: default
  html_notebook: default
---

# Computing Cmax test statistic

Cmax: denotes the maximum number of consecutive misses in a song
*(somewhat) works so that in songs where all of the misses are in the same region, there would be a higher probability of a longer string of consecutive misses (higher Cmax) than where the same number of misses would occur at random in a song of the same length.


```{r}
# function to take in a vector of 0s and 1s and calculate cmax
cmax <- function(v) {
  
  # set count.one to be 0
  count.one <- 0
  
  # set max to be empty vector
  max <- c()
  
  for (i in 1:length(v)) {

    # if it's a miss: count goes up, count is added to max vector, cmax takes the maximum of all values
    if (v[i] == 1) {
      count.one <- count.one + 1
      max[i] <- count.one
      } else {
    # if it's a hit count added is 0
        count.one <- 0
        max[i] <- 0
      }
    suppressWarnings(cmax <- max(max))
  }
  # return calculated value of cmax
  return(cmax)
}
```


```{r}
song.a <- c(1,0,0,0,0,0,1,0,1,0,0,1,0,0,0,0,1,0,0,0)
song.b <- c(0,0,0,1,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0)
song.c <- c(1,0,1,0,1,0,0,0,0,1,1,0,0,0,0,0,0)
song.d <- c(1,1,1,1,0,1,1,1,1,1,1,1,1,0,0,1,0)

cmax(song.a)
cmax(song.b)
cmax(song.c)
cmax(song.d)
```


# Method 1

Compute number of total misses over the number of miss streaks

```{r}
# function to take in a vector of 0s and 1s and calculate cmax
miss.over.streaks <- function(v) {
  
  count.one <- 0
  count.streaks <- 0
  num.miss <- c()
  counts <- c()
  
  for (i in 1:length(v)) {

    # if it's a miss: count goes up, count is added to counts vector, fills num.miss with a 1
    if (v[i] == 1) {
      count.one <- count.one + 1
      counts[i] <- count.one
      num.miss[i] <- 1
      } else {
    # if it's a hit count added is 0, count is added to counts vector, fills num.miss with a 0
        count.one <- 0
        counts[i] <- count.one + 0
        num.miss[i] <- 0
      }
    }
  for (j in 2:length(v)) {
    if (counts[j] == 0 && counts[j-1] != 0) {
      count.streaks <- count.streaks + 1
      } else {
        count.streaks <- count.streaks + 0
      }
  }
  prop <- sum(num.miss)/count.streaks
  # return calculated value of proportion
  return(prop)
}
```

```{r}
miss.over.streaks(song.a)
miss.over.streaks(song.b)
miss.over.streaks(song.c)
miss.over.streaks(song.d)
```

# Method 2

Compute the distance in between every miss

# count number of hits between misses
```{r}
numHits <- function(v) {
  # set number of hits to 0
  count.hit <- 0
  
  # make an empty vector
  hits <- c()
  
  for(i in 1:length(v)) {
    # if a hit, count increases 
    if(v[i] == 0) {
      count.hit <- count.hit + 1
      hits[i] <- count.hit
    }
    else
    {
      count.hit <- 0
      hits[i] <- count.hit
    }
    suppressWarnings(numHits <- hits)
  }
  
  return(numHits)
}
```

```{r}
song.a <- c(1,0,0,0,0,0,1,0,1,0,0,1,0,0,0,0,1,0,0,0)
song.b <- c(0,0,0,1,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0)
song.c <- c(1,0,1,0,1,0,0,0,0,1,1,0,0,0,0,0,0)
song.d <- c(1,1,1,1,0,1,1,1,1,1,1,1,1,0,0,1,0)
cat('Total Hits Between Misses: ' , numHits(song.a), '\n')
cat('Total Hits Between Misses: ' , numHits(song.b), '\n')
cat('Total Hits Between Misses: ' , numHits(song.c), '\n')
cat('Total Hits Between Misses: ' , numHits(song.d), '\n')
```


# Resampling WITHOUT Replacement
```{r}
n <- 1000
perm.resample <- function(v) {
  shuffled <- matrix(nrow=n, ncol=length(v))
  for (j in 1:length(v))
    for (i in 1:n) {
    shuffled[i,j] <- (sample(v, size = length(v), replace = FALSE))[j]
  }
  return(shuffled)
}
```

```{r}
samples.a <- perm.resample(song.a)
samples.b <- perm.resample(song.b)
samples.c <- perm.resample(song.c)
samples.d <- perm.resample(song.d)
```


# H-Test for Cmax
H0: The notes are missed randomly
H1: The notes are not missed randomly

## Test Cmax on Resampled Data
```{r}
cmax.test <- function(m, song) {
  cmax.vals <- c()
  for (i in 1:nrow(m)) {
    cmax.vals[i] <- cmax(m[i,])
  }
  cmax.test.stat <- cmax(song)
  pval <- 2*min(sum(cmax.vals >= cmax.test.stat), sum(cmax.vals <= cmax.test.stat))/1000
  return(pval)
}
```

## P-Value
```{r}
cmax.test(samples.a, song.a)
cmax.test(samples.b, song.b)
cmax.test(samples.c, song.c)
cmax.test(samples.d, song.d)
```

# H-Test Method 2

## Num of Misses / Num of Miss Streaks on Resampled Data
```{r}
method1.test <- function(m,song) {
  method1.vals <- c()
  for (i in 1:nrow(m)) {
    method1.vals[i] <- miss.over.streaks(m[i,])
  }
  method1.test.stat <- miss.over.streaks(song)
  pval <- 2*min(sum(method1.vals >= method1.test.stat), sum(method1.vals <= method1.test.stat))/1000
  return(pval)
}
```

## Pvalue
```{r}
method1.test(samples.a, song.a)
method1.test(samples.b, song.b)
method1.test(samples.c, song.c)
method1.test(samples.d, song.d)
```


# H-Test for Method 3
** Not working **
## NumHits on resampled Data
```{r}
samples.numHits <- function(m) {
  numHits.vals <- c()
  for (i in 1:nrow(m)) {
    numHits.vals[i] <- numHits(m[i,])
  }
  return(numHits.vals)
}
```

```{r}
method2.a <- samples.numHits(samples.a)
method2.b <- samples.numHits(samples.b)
method2.c <- samples.numHits(samples.c)
method2.d <- samples.numHits(samples.d)
```
distance vectors: 
song a - (1,4,2)
song.b - (5,2)
song.c - (2,6,3)
song.d - (1,1,1)



